Thread Pool in GeckoDB/BOLSTER - Implementing a Thread Pool for a High Performance Database System \\

### 2018-07-02 Presentations/Paper/paper_thread_pool.tex
Add Baseline compare to paper

			double results[numThreads];
			thread_task_t tasks[numThreads];

@@

Secondly, the task creation and enqueuing does not have heavy impact on the performance, since the difference in execution time \textbf{TODO: Complete!}

>>>>

			double results[numThreads];

@@

Secondly, the task creation and enqueuing have only slight on the performance, since the baseline does not include these operations, but is still clearly faster than the thread pool implementation.
